---
title: "NEWS-MIEGLEtools"
output: github_document
---

<!-- NEWS.md is generated from NEWS.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "NEWS-"
)
```

```{r, echo = FALSE}
cat(paste0("Last Update: ",Sys.time()))
```

MIEGLEtools v0.1.0.9001 (2020-07-28)
================

* Start adding elements to allow for package creation.
    + DESCRIPTION
        - Title, Description, authors, maintainer, IMPORTS, License, and URL
    + NEWS
        - Add file and update.
    + MIEGLEtools
        - Remove from base directory
    + .\inst\extdata\Notebook_MIEGLEtools.Rmd
        - Add notebook for code to aid in creation of package
    + Vignette
        - Ensure each chunk had a unique name (single word only).
    + runShiny.R
        - Update URL in details.
    + README
        - Need to add RMD file for editing only have MD.
* Shiny app updates
    + Add packages to DESCRIPTION.  
    + Comment out library() calls in ui.R and server.R.  
* License
    + Recreated with usethis::use_mit_license("Ben Block")
* Ran Check and addressed issues.
* UI.r, update version number to the same as the package version.

MIEGLEtools v0.1.0.9000 (2020-07-28)
================

* Forked code from https://github.com/Blocktt/MIEGLEtools
