---
title: "NEWS-MIEGLEtools"
output: github_document
---

<!-- NEWS.md is generated from NEWS.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "NEWS-"
)
```

```{r, echo = FALSE}
cat(paste0("Last Update: ",Sys.time()))
```

MIEGLEtools v0.1.2.902 (2020-08-10)
================
* Minor updates to make input columns correct format. Removed extra internal examples. 

MIEGLEtools v0.1.2.900 (2020-08-07)
================
* Added R leaflet map to Shiny app - local testing complete. The map requires metric scores to be calculated from input file prior to mapping.


MIEGLEtools v0.1.1.956 (2020-08-06)
================
* Added R leaflet map to Shiny app. Still in testing. The map requires metric scores to be calculated from input file prior to mapping. Attempting to make reactive.


MIEGLEtools v0.1.1.946 (2020-07-30)
================
* Fixed Issues #1 and #2 (see GitHub repo). The Shiny app crashed because metric.values.MI.R required certain columns that were not in the input data set. To combat this, we included a section in server.R that tacks on any missing columns onto the input data set prior to metric calculation using metric.values(). 
* Next steps are product testing and accuracy testing. 


MIEGLEtools v0.1.1.939 (2020-07-30)
================
* Took metric.values() function from `BioMonTools` and created a version that is saved within the Shiny app
* Updated server.R to reflect new metric values function:
df_metval <- suppressWarnings(metric.values.MI(fun.DF = df_data, fun.Community = "bugs", fun.MetricNames = MichMetrics, boo.Shiny = TRUE))


MIEGLEtools v0.1.1.934 (2020-07-28)
================
* Updated thresholds for metric scoring to be obtained from within the `BioMonTools` package
    + The `BioMonTools` package has a thresholds excel file within the package that is referenced. 
    + This Excel file would need to be edited to changed metric threshold values when scoring metrics. 
* Version changed to previous naming convention v0.1.1.934 rather than v0.1.0.9001. 

MIEGLEtools v0.1.0.9001 (2020-07-28)
================

* Start adding elements to allow for package creation.
    + DESCRIPTION
        - Title, Description, authors, maintainer, IMPORTS, License, and URL
    + NEWS
        - Add file and update.
    + MIEGLEtools
        - Remove from base directory
    + .\inst\extdata\Notebook_MIEGLEtools.Rmd
        - Add notebook for code to aid in creation of package
    + Vignette
        - Ensure each chunk had a unique name (single word only).
    + runShiny.R
        - Update URL in details.
    + README
        - Need to add RMD file for editing only have MD.
* Shiny app updates
    + Add packages to DESCRIPTION.  
    + Comment out library() calls in ui.R and server.R.  
* License
    + Recreated with usethis::use_mit_license("Ben Block")
* Ran Check and addressed issues.
* UI.r, update version number to the same as the package version.

MIEGLEtools v0.1.0.9000 (2020-07-28)
================

* Forked code from https://github.com/Blocktt/MIEGLEtools
