---
title: "MIEGLEtools"
author: "Ben.Block@tetratech.com"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MIEGLEtools}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
# Introduction
`MIEGLEtools` was created by Tetra Tech, Inc. in 2020 to meet the needs of Michigan Environment, Great Lakes and Energy (EGLE) staff to complete data manipulations in an efficient and reproducible manner. The core purpose of this package is to run a web-based Shiny application that uses the `BioMonTools` package to calculate metric values and scores. 

It is envisioned that this library will be a living program and will add additional functions and routines in the future.

# Installation

The R library is saved on GitHub (https://github.com/Blocktt/MIEGLEtools) for ease of updating and distribution.  Issues can be tracked, fixed, and code is available for download.  Current users of `MIEGLEtools` can update the library using the same code used to install the library (see below).  

Devtools is required to download from GitHub. The `MIEGLEtools` package uses the `BioMonTools` package to calculate metric values and scores - therefore, the `BioMonTools` package also needs to be downloaded from GitHub (see below).


At this time, there are no plans to submit `MIEGLEtools` to CRAN (R's library repository).
### `MIEGLEtools`, Download Instructions

```{r install, eval=FALSE}
install.packages("devtools")
library(devtools)
Sys.setenv("TAR" = "internal")  # needed for R v3.6.0
install_github("Blocktt/MIEGLEtools", force=TRUE, build_vignettes=TRUE)
```

### `BioMonTools`, Download Instructions

```{r install, eval=FALSE}
library(devtools) # assumes you already have devtools installed (see above)
Sys.setenv("TAR" = "internal")  # needed for R v3.6.0
install_github("Blocktt/BioMonTools", force=TRUE, build_vignettes=TRUE)
```

To contact the author directly email Ben.Block@tetratech.com.

# Packages
Several packages were used to build the functionality in `MIEGLEtools`:

`BioMonTools` 
`dplyr`


To install packages follow the example of the code below for installing `dplyr`.

```{r install example 2, eval=FALSE}
install.package("dplyr")
```


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MIEGLEtools)
```
